---
title: "Tidy Tuesday 2021-05-25 (Mario Kart)"
author: "Emily Williams"
date: "24/06/2021"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)

# Load relevant libraries
library(tidytuesdayR)
library(tidyverse)

# Get the Data
tuesdata <- tidytuesdayR::tt_load('2021-05-25')

#Separate the Data
records <- tuesdata$records
drivers <- tuesdata$drivers
rm(tuesdata)

```

## Mario Kart 64 World Records!

My research question ideas:

* What was the longest held record(s) and the shortest held records(s)? Separate out single and 3 lap (type).

* Compare record times for pre- and post- a certain time period. Maybe the median?

* **Added during:** Of records that got beat on the same day, how many seconds (and as a percentage) did the new record shave off?

```{r longest_and_shortest_held_records}

longest_held <- records %>%
  group_by(type) %>%
  filter(record_duration == max(record_duration)) %>%
  ungroup()

longest_held

shortest_held <- records %>%
  group_by(type) %>%
  filter(record_duration == min(record_duration)) %>%
  ungroup()

shortest_held

```

So whilst there is only 1 unique longest-held number of days for each type, there are many entries for the shortest-held number of days for each type (0). These reflect records that were broken the same day.

This is really interesting to me, so I'm going to now look at a new question:

* Of records that got beat on the same day, how many seconds (and as a percentage) did the new record shave off?

```{r same_day_new_records}

# so I need to find the records in 'records' that superceded those in 'shortest_held', by matching track, type, shortcut and date

# how do I do that?
# I could do a join, then add an ending to the new column names
# would have to remove the contents of shortest_held from records

records_excluding <- records %>%
  anti_join(shortest_held)
  
# done - now add columns to shortest_held that match track, type, shortcut and date from records

# note, where there is NA in the new columns, the new record was also broken that same day
# don't handle this for now

same_day_breaks <- shortest_held %>%
  left_join(records_excluding,
            by = c("track", "type", "shortcut", "date"),
            suffix = c("_original", "_new")) %>%
  #make a new column for the number of seconds shaved off, and as a percentage
  mutate(seconds_less = time_original - time_new,
         seconds_less_perc = seconds_less / time_original)

# plot this for each track, type and shortcut

ggplot(data = same_day_breaks, aes(x = track, y = seconds_less_perc)) +
  geom_bar(stat = "identity", fill = "blue") +
  geom_text(aes(label = seconds_less_perc), vjust = 1.6, color = "black", size = 3.5)+
  theme_minimal()

# leave it there for now - have only separated by track

```

